Penguins Search Optimisation Algorithm for Association Rules Mining

### 2015-02-09 Swarm paper/elsarticle/elsarticle-template-num.tex
finished

\documentclass[preprint,12pt]{elsarticle}
\usepackage{lscape}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}

@@

Association Rules Mining (ARM) is one of the most popular and well-known approaches for the decision-making process. All existing ARM algorithms generate a very large number of association rules with high overlapping. To deal with this issue, we propose a new ARM approach based on penguins search optimisation algorithm (Pe-ARM for short). Moreover, an efficient measure is incorporated into the main process to evaluate the amount of overlapping among the generated rules. Indeed, before the evaluation of the rules, each penguin calculates the amount of overlapping between its rule and all accepted rules. Then, the given rule is rejected without fitness evaluation if at least the amount of overlapping for this rule and one rule from the set of accepted rule is greater than the maximum accepted overlap. The proposed approach also ensures a good diversification over the whole solutions space thanks to the multi-groups behaviour of penguins. Furthermore, the search process is based on the oxygen reserve of each penguin, which permit to accelerate the search of a good solutions in a reasonable time and to save energy in the disagreeable regions. To demonstrate the effectiveness of the suggested approach, several experiments have been carried out on different data-sets and specifically on the biological ones. The results reveal that the proposed approach outperforms the well known ARM algorithms in both execution time and solution quality. 
\end{abstract}

@@

for swarm intelligence. These algorithms have the potential to \textbf{give only one part of rules and not all relevant rules}. Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of the extracted rules using meta-heuristics based approaches by taking into account the similar rules in the other hand. \\

@@

In this paper, a new algorithm called Pe-Arm (penguins search optimisation algorithm for association rules mining) is proposed  to find a set of consistent rules with superior quality and a low amount of overlapping among the rules. These set of rules must cover the maximum number of transaction in the database.\\

@@

\subsection{ARM with meta-heuristics}
Meta-heuristics have been used to reduce the run time of the existing ARM algorithms. Genetic algorithm is the first evolutionary algorithm used to solve the ARM problem, such as GENAR \cite{16}, GAR \cite{17}. 
Those two methods used the standard version of the genetic algorithm with poor representation of the \textbf{individuals}. Afterward, several methods 
for improving genetic algorithm for association rule mining have been proposed to ameliorate genetic operators and the 
representation of \textbf{individuals}, such as ARMGA \cite{10}. Two major differences between the classical GENAR and ARMGA are the mutation and crossover methods. Often a hybrid method is used to reduce cost, as well as to improve the original methods. A novel hybrid genetic based algorithm called PQGMA has been applied for association rules mining with the use of simulated annealing for the mutation and the crossover operations respectively.
Quantum computing based method \cite{18} uses an adaptive mutation rate, and provides a diversified population.
G3APRM \cite{11} is a novel generation \textcolor{red}{on} association rule mining algorithm with the use of  genetic programming based on the 
Grammar Guided Genetic Programming to avoid invalid individuals found by genetic programming process. In \cite{19}, 
the authors reviewed all association rule mining algorithms based on genetic algorithm and its hybridisation.

Other methods based on swarm intelligence have been designed for ARM problem. 
Particle swarm optimisation algorithm has been applied for association rule mining \cite{12}, 
in this algorithm particle moves randomly on different neighbourhood and optimise the selection process with the best neighbour. 
The main difference between this method and the AGA is the use of neighbourhood points which outperforms the \textcolor{red} {intensification search}. 
Other swarm intelligence algorithms have also been applied for ARM problem. Firstly, an Ant colony optimisation \cite{20} was employed in health application 
to deal with the health insurance database. ARMBGSA \cite{21} is an association rule mining algorithm based on Newton law of universal gravitation namely 
a gravitational emulation local search algorithm, which is a nature inspired optimisation algorithm. Each rule is modelled as a mass, all the masses attract each other using the law of motion. Each iteration is based on the 
previous one, and take only the k-heaviest masses in order to influence the new masses. The algorithm generates few rules because 
the search space is reduced at each iteration. 
Authors on \cite{22} proposed a new hybrid algorithm called (HBSO-TS) for association rule mining based on hybrid method based on 
Bees Swarm Optimisation (BSO) and Tabu Search (TS). BSO is used to explore the search space so that it can cover most of its neighbours.

@@

The population of penguins locates initial position \textbf{(solution space)}, then the population is divided into a set of groups, and each group is assigned to a region in the whole solution space. Each penguin then dives and swims under the water for hunting fish while consuming its oxygen reserve. Different forms of communication between penguins are occasionally \textbf{taken place} and the quantities of eaten fish increase. The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached. The authors of \cite{15} have shown that the PeSOA outruns genetic algorithms and particle swarm optimisation in obtaining better values for benchmark optimisation functions. 
After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuously
 improves as more members report the food sources. After an entire cycle of the intra-group communication of all the penguin groups, the penguins might migrate to other group's habitat according to the probability of nurture existence of each group in terms of the quantity of food found by all its members.
The oxygen reserve depends on both the gain of the food source and the swimming duration the penguin endures. If the energy gain is positive, the longer the penguin stays under the water, the more quantities of food it catches and thus becomes healthier. Otherwise, the longer the swimming duration, the more oxygen the penguin consumes. Hence, the oxygen reserve is updated according to the amelioration of the objective function. The oxygen reserve increases if the new solution is better than the previous one, and the oxygen reserve decreases in the other case.

@@

\textbf{Proof:}
\begin{enumerate}[i)]
\item  $\mu$($r_1$, $r_2$) = 0 if and only if $r_1$, $r_2$ agree in all items and this happens if
and only if $r_1$\{x\} = $r_2$\{x\} and $r_1$\{y\} = $r_2$\{y\}.
\item  The number of items in which $r_1$ differs from $r_2$ is equal to the number of
items in which $r_2$ differs from $r_1$, because the distance is equal to the sum of all items $\left|r_1\right|+\left|r_2\right|$.
\item  $\mu$($r_1$, $r_2$) is equal to the minimal number of items which change their position or to add necessary to get
from $r_1$ to $r_2$. In its turn, $\mu$($r_2$, $r_3$) is equal to the minimal number
of items changes position or \textcolor{red}{to add
necessary} to get from $r_2$ to $r_3$.\\
So $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) changes from $r_1$ to $r_3$. Hence \\
$\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) $\geq$ $\mu$($r_1$, $r_3$) which is the minimal number of
items that change position or \textcolor{red}{to add necessary} to get from $r_1$ to $r_3$.
\end{enumerate}
\textbf{Example:}
Let $I=\left\{A,B,C,D,E,F\right\}$ be a set of items and ($r_{1}$,$r_{2}$) are two rules defined as follow:\\
$r_{1}$ : A,B,C $\rightarrow $D\\
$r_{2}$ : C,D $\rightarrow$ E \\
$\mu$($r_{1},r_{2}$) = 3.5
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{3.jpg}
\end{center}
\label{Fig1}
\caption{Measuring overlap distance}
\end{figure}

\subsection{The Fitness Function}
The main goal of penguins search algorithm is to optimise the
expenditure of energy (run time) and to improve the
quality of generated rules. The generated rules have both
individual and collective quality, the first quality represents
the statistical measure (confidence and support) which is
calculated only from the rule and the transactional database,
whereas, the second one aims to represent the correlation between
the rules (overlap) which is well explained in the previous
section. In the fitness computing, we focused on the first aspect
by taking the rules which maximise the average of the support (Supp) and the confidence (Conf). The fitness value is computed only for the rules satisfying the maximum overlap where
the maximum Overlap (Max-Overlap) is a predefined value that represents the
maximum accepted distance between each pair of rules.
More formally, the fitness function $F$ for a given solution $S$
can be formulated as:\\
\begin{equation}
\label{equa:eq1} F_{max}(S)=\alpha Supp(S) + \beta Conf
(S)
\end{equation}
where\\

$Supp(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
\subseteq t,  \forall i \in [1..n]\}|}{|T|}$\\ \\
$Conf(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
S[i]\subseteq t, \forall i \in [1..n]\}|}{|\{t \in T | S[i]=1
\Rightarrow S[i]\subseteq t, \forall i \in [1..n]\|}$\\
\\
where
$\alpha$ and $\beta$ are two empirical parameters chosen between
$0$ and $1$ and $T$ is the transactional database.
\\
\textbf{Example:}
\begin{table}[h]
\centering
\begin{tabular}{c c c c}
\hline
$t_{1}$& A & B & C\\
\hline
$t_{2}$& A & B & \\
\hline
$t_{3}$& C & D & \\
\hline
$t_{4}$& E & D & \\
\hline
$t_{5}$& C & A &\\
\hline
\end{tabular}
\caption{Illustration of transactional database for fitness computing}
\label{TransacionalDatabaseIllustration}
\end{table}

@@

\subsection{Parameters Settings}
The Penguin search algorithm needs many parameters to ensure the diversification and the intensification properties of the search
process. The aim of this experiment is to find the best parameters to maximise the ratio 
between the average of the fitness of generated rules and the CPU run time. 
In each iteration, we change the parameters in order to find the best stabilised average values. Each new \textbf{parameter is} tested for a set of  datasets. As seen in table 2, when a fewer number of penguins are used the CPU run time is lower, consequently, 
a small part of the rules space is explored, this reduces the quality of the generated rules. In contrast, when the number of penguins 
increases, we get a set of good rules but with increased CPU run time (a 100 generation is used for all tests).

For the number of iterations (table 3), we aim to stabilise the average of the \textcolor {red}{fitness solutions with the execution time}. It is evident from the table that the fewer the number of iterations the smaller the average of confidence and support and the smaller the execution time. This due to the fact that with a fewer number of iterations a fewer number of rules are generated. However, if the number of iteration is increased the average of confidence and support also increased but with a longer execution time. According to the obtained results, 
the number of iterations is set to $100$ and the number of penguins is set to $25$.
\begin{landscape}
%\clearpage
\begin{table*}[b]
\caption{The performance of the PeSOA number of iterations with CPU execution time for different data sets.}
\label{sample-table}
\begin{tabular}{c c c c c c c c c c c c c c c c c c c}
\toprule
\textbf{Data sets} &  \multicolumn{2}{c}{Bolts} & \multicolumn{2}{c}{Sleep} & \multicolumn{2}{c}{Pollution}& \multicolumn{2}{c}{Basket-Ball}& \multicolumn{2}{c}{IBM-Quest}& \multicolumn{2}{c}{Quack}& \multicolumn{2}{c}{Chess}& \multicolumn{2}{c}{Mushroom}\\\midrule
{N Penguins}   & \textbf{F}  & \textbf{t}  & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} \\\hline                      
10		&		0.81 & 	0.03		& 		0.88 & 	0.24	&		0.79 & 0.21	&		0.91 & 	0.14		&	 0.81 &	0.19	& 0.81 &  0.54 &	0.80 &	0.61  &	0.78 & 	1.21 \\\hline
15		&		0.85 & 	0.05		& 		0.93 & 	0.31	&		0.91 & 0.28	&		0.95 & 	0.20		&	 0.86 & 0.21	& 0.89 &  0.61 &	0.83 &	0.70  &	0.79 &	1.41 \\\hline
20    &		0.98 & 	0.08		& 		0.97 & 	0.39	&		0.97 & 0.35	&		0.98 & 	0.29		&	 0.90 &	0.25	& 0.90 &  0.69 &	0.87 &	0.76  &	0.81 &  1.58	 \\\hline
25		&		0.99 & 	0.10		& 		0.99 & 	0.46	&		1    & 0.37	&	  0.99 & 	0.31	  &	 0.92 &	0.28	& 0.90 &  0.76 &	0.88 &  0.80  &	0.84 & 	1.67 \\\hline
30		&	  1    & 	0.13		& 		0.99 & 	0.52  &		1    & 0.44	&		0.99 & 	0.37		&	 0.92 &	0.35	& 0.90 &  0.82 &	0.88 &  0.87  &	0.84 &  1.72 \\\hline
35	  &		1    & 	0.18	  & 		0.99 & 	0.57	&		1    & 0.49	&		0.99 & 	0.44 	  &	 0.92 &	0.39	& 0.89 &  0.87 &	0.88 &  0.93  & 0.84 & 	1.79 \\\hline
40	  &		1    & 	0.21		& 		0.97 & 	0.62  &		1    & 0.56	&		0.98 & 	0.46		&	 0.91 &	0.42  & 0.90 &  0.93 &	0.87 &	0.99  &	0.84 & 	1.83 \\\hline
50		&		0.99 & 	0.25	  & 		0.99 & 	0.75	&		1    & 0.62	& 	0.98 & 	0.53		&	 0.92 &	0.56  & 0.90 &  1.10 &	0.88 &	1.15  &	0.82 & 	1.99 \\\hline
60		&		1    & 	0.30		& 		0.98 & 	0.82  &		1    & 0.81	&		0.99 & 	0.61		&	 0.92 &	0.63  & 0.90 &  1.25 &	0.88 &	1.32  &	0.84 & 	2.18 \\\hline
75		&		1    & 	0.41		& 		0.99 & 	0.91	&		1    & 0.95	&		0.99 & 	0.82		&	 0.92 &	0.75  & 0.90 &  1.39 &	0.88 &	1.49 &	0.84 & 	2.32 \\\hline
100		&		1    &  0.62		& 	  0.99 & 	1.14  &		1    & 1.24	&		0.99 & 	1.02		&	 0.92&	0.92  & 0.90 &  1.52 &  0.88 &	1.81 &	0.84 & 	2.61 \\\hline
\bottomrule
\end{tabular}
\end{table*}

@@

\bottomrule
\end{tabular}
\end{table*}
The main motivation behind using biological datasets for evaluation is the 
specificity of gene expression data sets that contains comprehensive and integrated biological information, 
enabling the discovery of functional relationships between those information. Tables 9,10 and 11 show that the coverage of the final set of association rules 
are very large comparing to other standard datasets according to the strong relation between biological data, also the coverage of Pe-ARM
(with overlap measure) is the best comparing with Pe-ARM
(without overlap measure) and BSO-ARM, and this large coverage can be interpreted with very low correlation between rules that allow to 
take all transaction and items on consideration. The confidence and support average of the Pe-ARM has been ameliorated since the use of the Pe-ARM.
In experimentation of biological data sets cases we have used 0.20, 0.30, 0.50 for minimum support, minimum confidence and minimum overlap accepted, respectively during performing experiments on standard datasets.

%% \begin{theorem}[ ] ...  \end{theorem}
%% \begin{definition}[ ] ...  \end{definition}
%% \begin{axiom}[ ] ...  \end{axiom}
%% \begin{conjecture}[ ] ...  \end{conjecture}
%% \begin{proposition}[ ] ...  \end{proposition}
%% \begin{corollary}[ ] ...  \end{corollary}
%% \begin{lemma}[ ] ...  \end{lemma}
%% \begin{problem}[ ] ...  \end{problem}
%% \begin{example}[ ] ...  \end{example}
%% \begin{remark}[ ] ...  \end{remark}
%% \begin{proof} ...  \end{proof}
%%
 \section{Conclusion}
In this work a new association rules mining algorithm based on penguins search optimisation 
algorithm (Pe-Arm) has been proposed. The incorporation of a new overlapping measure  into the main method of Pe-Arm to evaluate the amount of overlapping between generated rules in order to generate a set of consistent rules. 
Pe-Arm has been compared with a set of well known meta-heuristics for association rule mining, by different criteria such as the computational time, the statistical measure (confidence and support) and finally with the coverage measure, which proved the efficiency of the proposed Pe-ARM. Different data sets have been used in the comparison, firstly is the standard data is used to evaluate the approach with those datasets that have been used by most of the association rule mining algorithm. Secondly, with a biological datasets, the use of biological data sets allows us to validate the approach with data that contain a huge number of association between item sets which is the specificity of the gene expression data. The gene expression datasets is made for that raison like extracting rules between conditions of genes. Currently, we are investigating with the improvement of the rules representation to develop new way to represent large datasets because we lose a lot of time on measure calculation.

@@

\newpage
\section*{References}
\bibliography{mybibfile}

>>>>

\documentclass[preprint,12pt]{elsarticle}
\usepackage{pdflscape}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}

@@

Association Rules Mining (ARM) is one of the most popular and well-known approaches for the decision-making process. All existing ARM algorithms generate a very large number of association rules with high amount of overlapping. To deal with this issue, we propose a new ARM approach (Pe-ARM) based on penguins search optimisation algorithm (PeSOA). Moreover, a new method of overlapping measure is used in the Pe-ARM to evaluate the amount of overlapping among the generated rules. %Indeed, before the evaluation of the rules, each penguin calculates the amount of overlapping between its rule and all accepted rules. Then, the given rule is rejected without fitness evaluation if at least the amount of overlapping for this rule and one rule from the set of accepted rule is greater than the maximum accepted overlap. 
The proposed approach ensures a good diversification over the whole solution space by utilising the multi-groups behaviour of penguins. Furthermore, the search process is based on the oxygen reserve of each penguin, which helps to accelerate the search process. To demonstrate the effectiveness of the proposed approach, several experiments have been carried out on different datasets and specifically on the biological ones. The results reveal that the proposed approach outperforms different well-known ARM algorithms in both execution time and solution quality. 
\end{abstract}

@@

for swarm intelligence. These algorithms have the potential to give only a subset of all relevant rules. Therefore, two challenges can be derived, the computation time of exact algorithms by exploring all rules space in one hand and the quality of the extracted rules using meta-heuristics based approaches by taking into account the similar rules in the other hand. \\

@@

In this paper, a new algorithm called Pe-ARM (penguins search optimisation algorithm for association rules mining) is proposed  to find a set of consistent rules with superior quality and a low amount of overlapping among the rules. These set of rules must cover the maximum number of transaction in the database.\\

@@

\subsection{ARM with meta-heuristics}
Meta-heuristics have been used to reduce the run time of the existing ARM algorithms. Genetic algorithm is the first evolutionary algorithm used to solve the ARM problem, such as GENAR \cite{16}, GAR \cite{17}. 
Those two methods used the standard version of the genetic algorithm with poor representation of the solutions. Afterward, several methods 
for improving genetic algorithm for association rule mining have been proposed to ameliorate genetic operators and the 
representation of the solutions, such as ARMGA \cite{10}. Two major differences between the classical GENAR and ARMGA are the mutation and crossover methods. Often a hybrid method is used to reduce cost, as well as to improve the original methods. A novel hybrid genetic based algorithm called PQGMA has been applied for association rules mining with the use of simulated annealing for the mutation and the crossover operations respectively.
Quantum computing based method \cite{18} uses an adaptive mutation rate, and provides a diversified population.
G3APRM \cite{11} is a new method for association rule mining  with the use of  genetic programming based on the 
Grammar Guided Genetic Programming to avoid invalid individuals found by genetic programming process. In \cite{19}, 
the authors reviewed all association rule mining algorithms based on genetic algorithm and its hybridisation.

Other methods based on swarm intelligence have been designed for ARM problem. 
Particle swarm optimisation algorithm has been applied for association rule mining \cite{12}, 
in this algorithm particle moves randomly on different neighbourhood and optimise the selection process with the best neighbour. 
The main difference between this method and the AGA is the use of neighbourhood points to improve the search intensification strategy. 
Other swarm intelligence algorithms have also been applied for ARM problem. Firstly, an Ant colony optimisation \cite{20} was employed in health application 
to deal with the health insurance database. ARMBGSA \cite{21} is an association rule mining algorithm based on Newton law of universal gravitation namely 
a gravitational emulation local search algorithm, which is a nature inspired optimisation algorithm. Each rule is modelled as a mass, all the masses attract each other using the law of motion. Each iteration is based on the 
previous one, and take only the k-heaviest masses in order to influence the new masses. The algorithm generates few rules because 
the search space is reduced at each iteration. 
Authors on \cite{22} proposed a new hybrid algorithm called (HBSO-TS) for association rule mining based on hybrid method based on 
Bees Swarm Optimisation (BSO) and Tabu Search (TS). BSO is used to explore the search space so that it can cover most of its neighbours.

@@

The population of penguins locates initial position (solution space), then the population is divided into a set of groups, and each group is assigned to a region in the whole solution space. Each penguin then dives and swims under the water for hunting fish while consuming its oxygen reserve. Different forms of communication between penguins are occasionally taken place and the quantities of eaten fish increase. The process is repeated until the specified amount of fish is obtained or the maximum number of iterations is reached. The authors of \cite{15} have shown that the PeSOA outruns genetic algorithms and particle swarm optimisation in obtaining better values for benchmark optimisation functions. 
After a number of dives, the penguin returns to surface and share with its group affiliates the position and quantity of the food found. So the local best of each group continuously
 improves as more members report the food sources. After an entire cycle of the intra-group communication of all the penguin groups, the penguins might migrate to other group's habitat according to the probability of nurture existence of each group in terms of the quantity of food found by all its members.
The oxygen reserve depends on both the gain of the food source and the swimming duration the penguin endures. If the energy gain is positive, the longer the penguin stays under the water, the more quantities of food it catches and thus becomes healthier. Otherwise, the longer the swimming duration, the more oxygen the penguin consumes. Hence, the oxygen reserve is updated according to the amelioration of the objective function. The oxygen reserve increases if the new solution is better than the previous one, and the oxygen reserve decreases in the other case.

@@

\textbf{Proof:}
\begin{enumerate}[i)]
\item  $\mu$($r_1$, $r_2$) = 0 if and only if $r_1$, $r_2$ agree in all items and this happens if
and only if $r_1$\{x\} = $r_2$\{x\} and $r_1$\{y\} = $r_2$\{y\}.
\item  The number of items in which $r_1$ differs from $r_2$ is equal to the number of
items in which $r_2$ differs from $r_1$, because the distance is equal to the sum of all items $\left|r_1\right|+\left|r_2\right|$.
\item  $\mu$($r_1$, $r_2$) is equal to the minimal number of items which change their position or to add necessary to get
from $r_1$ to $r_2$. In its turn, $\mu$($r_2$, $r_3$) is equal to the minimal number
of items changes their positions or number of items added
to obtain  $r_3$ from $r_2$.\\
So $\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) changes from $r_1$ to $r_3$. Hence \\
$\mu$($r_1$, $r_2$) + $\mu$($r_2$, $r_3$) $\geq$ $\mu$($r_1$, $r_3$) which is the minimal number of
items that changes their positions or number of items added
to obtain  $r_3$ from $r_1$.
\end{enumerate}
\textbf{Example:}
Let $I=\left\{A,B,C,D,E,F\right\}$ be a set of items and ($r_{1}$,$r_{2}$) are two rules defined as follow:\\
$r_{1}$ : A,B,C $\rightarrow $D\\
$r_{2}$ : C,D $\rightarrow$ E \\
The amount of overlapping between $r_{1}$ and $r_{2}$ is (see Fig. 1):\\
$\mu$($r_{1},r_{2}$) = 3.5 
\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.5]{3.jpg}
\end{center}
\label{Fig1}
\caption{Measuring overlap distance}
\end{figure}

\subsection{The Fitness Function}
The main goal of penguins search algorithm is to optimise the
expenditure of energy (run time) and to improve the
quality of generated rules. The generated rules have both
individual and collective quality, the first quality represents
the statistical measure (confidence and support) which is
calculated only from the rule and the transactional database,
whereas, the second one aims to represent the correlation between
the rules (overlap) which is well explained in the previous
section. In the fitness computing, we focused on the first aspect
by taking the rules which maximise the average of the support (Supp) and the confidence (Conf). The fitness value is computed only for the rules satisfying the maximum overlap where
the maximum Overlap (Max-Overlap) is a predefined value that represents the
maximum accepted distance between each pair of rules.
More formally, the fitness function $F$ for a given solution $S$
can be formulated as:\\
\begin{equation}
\label{equa:eq1} F_{max}(S)=\alpha Supp(S) + \beta Conf
(S)
\end{equation}
where $\alpha$ and $\beta$ are two empirical parameters chosen between
$0$ and $1$ and $T$ is the transactional database and \\
\begin{equation*}
Supp(S)= \frac{|\{t \in T | S[i] \neq 0 \Rightarrow S[i]
\subseteq t,  \forall i \in [1..n]\}|}{|T|}
\end{equation*}
\begin{equation*}
Conf(S)= \frac{|\{t \in T | S[i]\neq 0 \Rightarrow
S[i]\subseteq t, \forall i \in [1..n]\}|}{|\{t \in T | S[i]=1
\Rightarrow S[i]\subseteq t, \forall i \in [1..n]\|}\\
\end{equation*}
\\
\textbf{Example:}
\begin{table}[h]
\centering
\begin{tabular}{c c c c}
\hline
$t_{1}$& A & B & C\\
\hline
$t_{2}$& A & B & \\
\hline
$t_{3}$& C & D & \\
\hline
$t_{4}$& E & D & \\
\hline
$t_{5}$& C & A &\\
\hline
\end{tabular}
\caption{Illustration of transactional database for fitness computing}
\label{TransacionalDatabaseIllustration}
\end{table}

@@

\subsection{Parameters Settings}
The Penguin search algorithm needs many parameters to ensure the diversification and the intensification properties of the search
process. The aim of this experiment is to find the best parameters to maximise the ratio 
between the average of the fitness of generated rules and the CPU run time. 
In each iteration, we change the parameters in order to find the best stabilised average values. As seen in table 2, when a fewer number of penguins are used the CPU run time is lower, consequently, 
a small part of the rules space is explored, this reduces the quality of the generated rules. In contrast, when the number of penguins 
increases, we get a set of good rules but with increased CPU run time (a 100 generation is used for all tests).

For the number of iterations (table 3), we aim to stabilise the average between the fitness of the solutions and the execution time. It is evident from the table that the fewer the number of iterations the smaller the average of confidence and support and the smaller the execution time. This due to the fact that with a fewer number of iterations a fewer number of rules are generated. However, if the number of iteration is increased the average of confidence and support also increased but with a longer execution time. According to the obtained results, 
the number of iterations is set to $100$ and the number of penguins is set to $25$.
\begin{landscape}
%\clearpage
\begin{table*}[b]
\renewcommand{\arraystretch}{1.3}
\caption{The performance of the PeSOA number of iterations with CPU execution time for different data sets.}
\label{sample-table}
\begin{tabular}{c c c c c c c c c c c c c c c c c c c}
\toprule
\textbf{Data sets} &  \multicolumn{2}{c}{Bolts} & \multicolumn{2}{c}{Sleep} & \multicolumn{2}{c}{Pollution}& \multicolumn{2}{c}{Basket-Ball}& \multicolumn{2}{c}{IBM-Quest}& \multicolumn{2}{c}{Quack}& \multicolumn{2}{c}{Chess}& \multicolumn{2}{c}{Mushroom}\\\midrule
{N Penguins}   & \textbf{F}  & \textbf{t}  & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} & \textbf{F}  & \textbf{t} \\\hline                      
10		&		0.81 & 	0.03		& 		0.88 & 	0.24	&		0.79 & 0.21	&		0.91 & 	0.14		&	 0.81 &	0.19	& 0.81 &  0.54 &	0.80 &	0.61  &	0.78 & 	1.21 \\\hline
15		&		0.85 & 	0.05		& 		0.93 & 	0.31	&		0.91 & 0.28	&		0.95 & 	0.20		&	 0.86 & 0.21	& 0.89 &  0.61 &	0.83 &	0.70  &	0.79 &	1.41 \\\hline
20    &		0.98 & 	0.08		& 		0.97 & 	0.39	&		0.97 & 0.35	&		0.98 & 	0.29		&	 0.90 &	0.25	& 0.90 &  0.69 &	0.87 &	0.76  &	0.81 &  1.58	 \\\hline
25		&		0.99 & 	0.10		& 		0.99 & 	0.46	&		1    & 0.37	&	  0.99 & 	0.31	  &	 0.92 &	0.28	& 0.90 &  0.76 &	0.88 &  0.80  &	0.84 & 	1.67 \\\hline
30		&	  1    & 	0.13		& 		0.99 & 	0.52  &		1    & 0.44	&		0.99 & 	0.37		&	 0.92 &	0.35	& 0.90 &  0.82 &	0.88 &  0.87  &	0.84 &  1.72 \\\hline
35	  &		1    & 	0.18	  & 		0.99 & 	0.57	&		1    & 0.49	&		0.99 & 	0.44 	  &	 0.92 &	0.39	& 0.89 &  0.87 &	0.88 &  0.93  & 0.84 & 	1.79 \\\hline
40	  &		1    & 	0.21		& 		0.97 & 	0.62  &		1    & 0.56	&		0.98 & 	0.46		&	 0.91 &	0.42  & 0.90 &  0.93 &	0.87 &	0.99  &	0.84 & 	1.83 \\\hline
50		&		0.99 & 	0.25	  & 		0.99 & 	0.75	&		1    & 0.62	& 	0.98 & 	0.53		&	 0.92 &	0.56  & 0.90 &  1.10 &	0.88 &	1.15  &	0.82 & 	1.99 \\\hline
60		&		1    & 	0.30		& 		0.98 & 	0.82  &		1    & 0.81	&		0.99 & 	0.61		&	 0.92 &	0.63  & 0.90 &  1.25 &	0.88 &	1.32  &	0.84 & 	2.18 \\\hline
75		&		1    & 	0.41		& 		0.99 & 	0.91	&		1    & 0.95	&		0.99 & 	0.82		&	 0.92 &	0.75  & 0.90 &  1.39 &	0.88 &	1.49 &	0.84 & 	2.32 \\\hline
100		&		1    &  0.62		& 	  0.99 & 	1.14  &		1    & 1.24	&		0.99 & 	1.02		&	 0.92&	0.92  & 0.90 &  1.52 &  0.88 &	1.81 &	0.84 & 	2.61 \\\hline
\bottomrule
\end{tabular}
\end{table*}

@@

\bottomrule
\end{tabular}
\end{table*}

The main motivation behind using biological datasets for evaluation is the 
specificity of gene expression datasets that contains comprehensive and integrated biological information, 
enabling the discovery of functional relationships between those information. Tables 9 shows that the maximum confidence and support for the rules are obtained by using the proposed approach. Interestingly, although the Pe-ARM provides maximum average confidence and support but it takes the minimum amount of run time with compared to other approaches (see Table 10). It is evident from Table 11 that the Pe-ARM provides maximum coverage among all other approaches. It is also seen that the coverage of the final set of association rules for the dataset Elutriation 
is very high as well as the average confidence and support. This can be interpreted as: the set of generated rules are diverse and cover maximum number of different transactions. This is very important for biological datasets because they can grow very large and consist of small items therefore require more coverage. From the results shown in table 9, 10, and 11 we can conclude that the Pe-ARM approach outperforms all other approaches in all regards (e.g. execution time, coverage etc.).
%The confidence and support average of the Pe-ARM has been ameliorated since the use of the Pe-ARM.

%In experimentation of biological data sets cases we have used 0.20, 0.30, 0.50 for minimum support, minimum confidence and minimum overlap accepted, respectively during performing experiments on standard datasets.

%% \begin{theorem}[ ] ...  \end{theorem}
%% \begin{definition}[ ] ...  \end{definition}
%% \begin{axiom}[ ] ...  \end{axiom}
%% \begin{conjecture}[ ] ...  \end{conjecture}
%% \begin{proposition}[ ] ...  \end{proposition}
%% \begin{corollary}[ ] ...  \end{corollary}
%% \begin{lemma}[ ] ...  \end{lemma}
%% \begin{problem}[ ] ...  \end{problem}
%% \begin{example}[ ] ...  \end{example}
%% \begin{remark}[ ] ...  \end{remark}
%% \begin{proof} ...  \end{proof}
%%
 \section{Conclusion}
In this work a new association rules mining algorithm based on penguins search optimisation 
algorithm (Pe-ARM) has been proposed. To evaluate the amount of overlapping between generated rules, a new way of overlapping measure is incorporated into the main method of the Pe-ARM.  This incorporation helps to generate a set of consistent rules. 
Pe-ARM has been compared with a set of well known meta-heuristics based methods for association rule mining. The comparison was made to evaluate the performance of different methods in terms of computational time, the statistical measure (confidence and support) and finally the coverage measure. Two different types of datasets, e.g., standard and biological, were used to help the evaluation process. The use of biological data sets allows us to validate the approach with data that contain a huge number of association between item sets. The gene expression datasets are made to facilitate different functionalities like extracting rules between conditions of genes. The experiments confirm that the proposed Pe-ARM outperforms all other approaches in terms of statistical measure, coverage, and execution time for both standard and biological datasets. 
Currently, we are investigating to develop a new method to represent large data to further improve the execution time.

@@

\section*{References}
\bibliography{mybibfile}
